---
title: "linear model from Web"
author: "Cynthia Cornejo"
date: "Summer 2023"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
basicNN <- ggplot(data, aes(y = SIMS, x = ARM)) +
  geom_point() +
  labs(title = "SIMS and ARM") +
  theme(plot.title = element_text(hjust = 0.5))
basicNN
```

When we look at the graphs, we can easily see the comparison between the ARMS and SIMS data. There are a lot of dots, which means they are related in a positive way.

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

The numbers we got for SIMS~ARM is 0.6860073. This indicates a reasonable connection between the strengths of the two variables.

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

Examining the residual standard error, we find it to be 1.226. The R-squared value is 0.4706, and the adjusted R-squared value is 0.467. Adding more variables to the model may incur a penalty, but the multiple R-squared value remains unaffected, demonstrating its stability.

#### Predict at target point


```{r}
mydata <- data.frame(GRIP=94, ARM=88)
predict.lm(model.1, mydata, interval="prediction")
```

The predicted value came out to be 0.7063836. The lowest value observed is -1.726209, while the highest value recorded is 3.138977.

#### scatterplot with model fit
  
```{r}
basicNN <- ggplot(data, aes(y = SIMS, x = ARM)) +
  geom_point() +
  labs(title = "SIMS and ARM") +
  theme(plot.title = element_text(hjust = 0.5))
basicNN +
geom_smooth(method=lm)
``` 

This plot has a line showing the correlation. 

## Model 2 SIM~GRIP

### Now add in scatterplot

```{r}
mygrip <- ggplot(data, aes(y = SIMS, x = GRIP)) +
  geom_point() +
  labs(title = "SIMS and GRIP") +
  theme(plot.title = element_text(hjust = 0.5))
mygrip
```

In this graph we are now looking at SIMS and GRIP.

### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```

The numerical outcome for SIMS and grip is 0.6398458. This value is lower compared to the previous results, indicating that they have a weaker correlation between them.

### Inferential  (Build model.2)
  
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

The residual standard error stands at 1.295, accompanied by an adjusted R-squared of 0.4053. Thus far, it appears that the correlation between SIMS~GRIP is not as strong as the relationship observed between SIMS~ARM.

#### predict model.2 at target point

```{r}
predict.lm(model.2, mydata, interval="prediction")
```

The interval is now -3.107961 to 2.035652. 

#### now add the model fit to our plot for model.2
  
```{r}
mygrip <- ggplot(data, aes(y = SIMS, x = GRIP)) +
  geom_point() +
  labs(title = "SIMS and GRIP") +
  theme(plot.title = element_text(hjust = 0.5))
mygrip +
geom_smooth(method=lm)
``` 

This is with a model fit line to show correlation. 

## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
```
  
The correlation is larger than SIMS~GRIP and SIMS~ARM. With all three added up, the numerical results are 0.7326545.
  
### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

In this particular model, the residual standard error is 1.144, and the adjusted R-squared is 0.5358. Notably, this model exhibits the most favorable residual error when compared to the other models. The model equation is given by SIMS = 0.037311 * ARM + 0.024470 * GRIP - 5.433871.

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

